CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex

The classifiers that we attempted were
\begin{itemize}
\item support vector machines (SVM),
\item Fisher Discriminant Analysis (FDA),
\item Spectral Regression Discriminant Analysis (SRDA) and
\item Penalized Discriminant Analysis (PDA)
\end{itemize}

@@

%We tried these classifiers separately rather than 
We ended using just the SRDA classifier since the others were throwing memory errors.
\section{Results}

>>>>

The classifiers that we attempted were
\begin{itemize}
\item Support Vector Machines (SVM),
\item Fisher Discriminant Analysis (FDA),
\item Spectral Regression Discriminant Analysis (SRDA) and
\item Penalized Discriminant Analysis (PDA)
\end{itemize}

@@

%We tried these classifiers separately rather than 
%We ended using just the SRDA classifier since the others were throwing memory errors.
The implementation of these classifiers in mlpy required too much memory for
us to run the models on the all of the candidate answers. We used two main approaches
to solve these problems.
\begin{itemize}
\item We used SRDA because it seemed to handle the largest sample size.
\item We created a decision list from some of our answer evaluators. We ran the anwers
through this decision list before sending them to the SRDA learning algorithm.
\end{itemize}

\section{Results}
